\documentclass[margin,line]{res}

\usepackage{amssymb, amsthm, amsmath, amsfonts}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Nicholas C Rubert \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Wisconsin Institutes for Medical Research & {\it Voice:} (607) 425-1916 \\
1111 Highland Avenue, Room 1005 & {\it E-mail:} rubert@wisc.edu \\
Madison, WI 53705 USA \\
\end{tabular}

\section{\sc Education}
{\bf University of Wisconsin-Madison}, Madison, WI \\
\vspace*{-.1in}
\begin{list1}
\item[] PhD. in Medical Physics, Expected 2013
\vspace*{.05in}
\end{list1}

{\bf University of Wisconsin-Madison}, Madison, WI \\
\vspace*{-.1in}
\begin{list1}
\item[] M.S. in Medical Physics, August 2010
\vspace*{.05in}

\end{list1}

{\bf Pennsylvania State University}, State College, Pennsylvania\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S. in Physics, May 2008

\begin{list2}
 \vspace*{.05in}
 \item Minor: Mathematics, Chemistry, French
\end{list2}
\end{list1}

\section{\sc Experience}

{\bf University of Wisconsin-Madison}, Madison, WI \\
{\bf  Research Assistant} \hfill {\bf June 2008 - Present} \\
\vspace{-.2cm}
\begin{list2}
\item Implemented correlation based block matching algorithms and performed motion tracking on image sequences of ultrasound data.
\item Recorded sequences of ultrasound data of tissue mimicking phantoms and RF ablations in pig and rabbit liver under open surgery conditions.
\item Segmented stiffness images manually and with a morphological operator based automated segmentation algorithm developed in lab. 
\item Performed finite element simulation of linear, elastic mechanical models using ANSYS software.
\item Used finite element derived motion fields with a frequency domain simulation of ultrasound image formation
 to provide simulated ultrasound images for testing a novel block matching algorithm. 
\item Altered frequency domain based ultrasound simulations written in C++ to expose simulation variables to end users with only pre-compiled binaries.
\end{list2}

\vspace{.2cm}

{\bf UW Hospitals and Clinics }, Madison, WI \\
{\bf Radiotherapy Quality Assurance Volunteer} \hfill {\bf September 2010 - August 2011} \\
\vspace{-.2cm}
\begin{list2}
\item Performed quality assurance checks on Tomotherapy patient plans.
\item Performed ion chamber measurements and made comparisons with radiation doses predicted by treatment planning software.
\item Developed film used to verify doses delivered in Tomotherapy quality assurance checks.
\end{list2}

\vspace{.2cm}


{\bf Pennsylvania State University}, State College, PA \\
{\bf Tutor} \hfill {\bf September 2006 - May 2008} \\
\vspace{-.2cm}
\begin{list2}
\item Tutored college students in single and multi-variable calculus, differential equations, linear algebra, calculus-based physics, and algebra-based physics.
\item Reviewed homework problems and helped prep for exams with individual students and groups of students.
\end{list2}

\vspace{.2cm}

\nopagebreak[4]{
{\bf Pennsylvania State University}, State College, PA \\
{\bf Undergraduate Research Assistant}  \hfill {\bf August 2007 - May 2008} \\
\vspace{-.2cm}
\begin{list2}
\item Assisted graduate student with experiments in conductivity monitoring of underground aquifers.
\end{list2}
}

\section{\sc Software and Programming}
{\bf Software}
\begin{list2}
\item Matlab, Python, ImageJ, QT, Git, Latex, Bash, Paraview
\end{list2}

{\bf Projects}
\begin{list2}
\item Created QT GUI using C++ for display of ultrasound images and motor control of a volumetric ultrasound transducer.
\item In matlab, implemented a scan conversion from hardware dependent nonlinear coordinate system to Cartesian coordinates for visualization of 
      three-dimensional data in Paraview, a general purpose volume viewing software.
\item Replaced an undocumented random number generation algorithm with the tr1 random number generation, and an undocumented complex number class with a standard C++ class in a frequency domain ultrasound simulation program developed at the University of Wisconsin-Madison. 
\item Implemented correlation based block matching algorithms in C++, Python and Matlab.
\item Created finite element models using Q4, Q8, Q9, and linear triangular elements for linear elasticity problems in Matlab.
\end{list2}


\section{\sc Publications and Manuscripts}

Rubert, N; Bharat, S; Dewall R.J.; Andreano, A.; Brace, C.; Jiang, J.; Sampson, L.; Vargese, T.  Electrode displacement strain imaging of thermally-ablated liver tissue in an in vivo animal model.  Medical physics. Vol 37, p. 1075, 2010.

McCormick, M; Rubert, N; Varghese, T. Bayesian Regularization Applied to
Ultrasound Strain Imaging. IEEE Transactions on Biomedical Engineering.
In Press. 2011.

Nam, K; Rosado-Mendez, I.M.; Rubert, N.; .  Effects of Sound Speed Mismatch on Ultrasound Attenuaton Measurements Using a Reference Phantom.  	{\it In submission}

Jiang, J; Brace, C; Andreano, A; Dewall, R.J.; Rubert, N.; Fisher, T.G; Varghese, T.; Lee Jr., F.; Hall, T.J.;  Ultrasound-based relative elastic modulus imaging for visualizing thermal ablation zones in a porcine animal model.  Physics in Medicine and Biology.  Vol. 55.  March, 2010.


\section{\sc Conference Presentations}

Electrode displacement based strain imaging for monitoring in vivo open surgery thermal ablation therapies.  Rubert, N.; Bharat, S.; Dewall, R.J.; Andreano, A.; Brace, C.; Jiang, J.; Sampson, L.; Varghese, T. International Conference on the Ultrasonic Measurement and Imaging of Tissue Elasticity.  October 16, 2010.

Three dimensional strain imaging using electrode displacement strain imaging. Rubert, N.; Dewall, R.J.; Bharat S.; Varghese, T., Brace, C.; Andreano, A.; Hall, T.J.; Zagzebski, J.A.; Lee Jr., F.T.  Ultrasonic Imaging and Tissue Characterization Symposium.  June 10, 2009.

\end{resume}
\end{document}
