\documentclass[margin,line]{res}

\usepackage{amssymb, amsthm, amsmath, amsfonts}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Nicholas C Rubert \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Wisconsin Institutes for Medical Research & {\it Voice:} (607) 425-1916 \\
1111 Highland Avenue, Room 1005 & {\it E-mail:} rubert@wisc.edu \\
Madison, WI 53705 USA \\
\end{tabular}


\section{\sc Objective}
Medical physics research.

\section{\sc Education}
{\bf University of Wisconsin-Madison} \\
\vspace*{-.1in}
\begin{list1}
\item[] M.S. in Medical Physics, ????? 2010
\begin{list2}
\vspace*{.05in}
\item GPA: ?????/4.0
\end{list2}
\vspace*{.05in}

\end{list1}

{\bf Pennsylvania State University} State College, Pennsylvania, USA\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S. in Physics, May, 2008

\begin{list2}
 \vspace*{.05in}
 \item Minor: Mathematics, Chemistry, French
\end{list2}
\end{list1}

{\bf Athens Area High School},Athens, Pennsylvania USA\\
\vspace*{-.1in}
\begin{list1}
\item[] Graduated May, 2003
\end{list1}

\section{\sc Experience}

{\bf University of Wisconsin-Madison}, USA

\vspace{-.3cm}
{\em Research Assistant} \hfill {\bf June 2008 - Present} \\
Research diagnostic medical ultrasound stiffness imaging methods for measuring the extent of thermal ablations in the liver.

\vspace{-.3cm}
{\em Team Tomo Volunteer} \hfill {\bf August 2002 - May 2005} \\
Performed quality assurance checks on Tomotherapy patient plans.  Ensured Tomotherapy equipment was able to deliver the intended 
treatment plan through film and ion chamber measurements.

\vspace{-.3cm}
{\em Tutor} \hfill {\bf August 2002 - May 2005} \\
Tutor college students in single and multi-variable calculus, differential equations, linear algebra, and introductory physics.


\section{\sc Publications and Manuscripts}

{\bf Rubert, N}; Bharat, S; Dewall R.J.; Andreano, A.; Brace, C.; Jiang, J.; Sampson, L.; Vargese, T.  Electrode displacement strain imaging of thermally-ablated liver tissue in an in vivo animal model.  Medical physics. Vol 37, p. 1075, 2010.

McCormick, M; {\bf Rubert, N}; Varghese, T. Bayesian Regularization Applied to
Ultrasound Strain Imaging. IEEE Transactions on Biomedical Engineering.
In Press. 2011.

Nam, K; Rosado-Mendez, I.M.; {\bf Rubert, N.}; .  Effects of Sound Speed Mismatch on Ultrasound Attenuaton Measurements Using a Reference Phantom.  	{\it In submission}

Jiang, J; Brace, C; Andreano, A; Dewall, R.J.; {\bf Rubert, N.}; Fisher, T.G; Varghese, T.; Lee Jr., F.; Hall, T.J.;  Ultrasound-based relative elastic modulus imaging for visualizing thermal ablation zones in a porcine animal model.  Physics in Medicine and Biology.  Vol. 55.  March, 2010.


\section{\sc Conference Presentations}

Electrode displacement based strain imaging for monitoring in vivo open surgery thermal ablation therapies.  Rubert, N.; Bharat, S.; Dewall, R.J.; Andreano, A.; Brace, C.; Jiang, J.; Sampson, L.; Varghese, T. International Conference on the Ultrasonic Measurement and Imaging of Tissue Elasticity.  October 16, 2010.

Three dimensional strain imaging using electrode displacement strain imaging.  Rubert, Nicholas, Dewall, R.J., Bharat S., Varghese, Tomy, Brace, C., Andreano, A., Hall, T.J., Zagzebski, J.A., Lee Jr., F.T.  Ultrasonic Imaging and Tissue Characterization Symposium.  June 10, 2009.




\section{\sc Computer Skills}
\begin{list2}
\item Languages: C++, Python, Matlab.
\item Operating Systems: Linux, Windows.\\
\item Software: Qt, Git, Latex   
\end{list2}
\vspace*{-.15in}

\end{resume}
\end{document}
